Implementing a Capability Machine model into Iris

### 2020-01-13 prisc-2020-talk/slides.tex
progress on bonus slides that show the load case of the ftlr
finished Load case sketch in bonus slides

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{IEEEtrantools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{iris}

@@

~\\[0.5em]
\textbf{What's new: Iris formalization viewpoint}
\begin{itemize}
	\item Formalization of a machine level language, with no distinction between program and memory
	\item Distinction between  well-bracketed and non well-bracketed calls: using public/private transitions
\end{itemize}

@@

>>>>

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{tikz}
\usetikzlibrary{matrix}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{IEEEtrantools}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{longtable}
\usepackage{mathtools}
\usepackage{iris}
\usepackage{arydshln}
\usepackage[thinlines]{easytable}

@@

~\\[0.5em]
\textbf{What's new: Iris formalization viewpoint}
\begin{itemize}
	\item Formalization of a machine language, with no distinction between program and memory
	\item Distinction between well-bracketed and non well-bracketed calls: using public/private transitions
\end{itemize}

@@

{\small
\begin{table}
\begin{tabular}[t]{c}
\parbox{8cm}{\begin{align}
\only<4->{& decode(w) = \text{Load}~dst~src}
\only<1-3>{\\ &\bigsep_{a \in [b,e]} \text{read\_write\_cond }a}
\only<1-4>{\\ &\bigsep \mathcal{R}(r)}
\only<5->{\\ &\bigsep \mathcal{V}(p,g,b,e,a)}
\only<6->{\\ &\bigsep  \mathcal{V}(w_{src})}
\end{align}} \\[1em]
\hdashline
\parbox{8cm}{\begin{align}
\only<1-4>{&\bigsep_{reg \hookrightarrow w \in r\only<2->{\backslash \textsc{PC}}} reg \mapsto_r w}
\only<5->{&\bigsep dst \mapsto_r \only<5-6>{w_{dst}} \only<7->{\color{red} w_{src}} \\
				  &\bigsep src \mapsto_r (p,g,b,e,a)}
\only<2->{\\ &\bigsep \textsc{PC} \mapsto_r (pc_g,pc_p,pc_b,pc_e,pc_a)}
\only<3->{\\ &\bigsep pc_a \mapsto_a[pc_p] w}
\only<6->{\\ &\bigsep a \mapsto_a[p] w_{src}}
\end{align}} \\
\hline
\parbox{8cm}{\begin{align*}\textsc{WP}~\textsf{Seq (Instr Executable)}~
 		\{ v, &v = HaltedV \implies \\ &\exists \Sigma ' r',
 		\Sigma ' \sqsupseteq_{priv} \Sigma * {\textsf{context}(\Sigma ')(r')}\}
 		\end{align*}}
\end{tabular}
\end{table}
}
